\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{stmaryrd}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\author{Alice {\sc Pellet-Mary}}
\title{No Time To Say Hello}
\begin{document}

\maketitle

The clock in front of me rings. Five o'clock. The hands never stop, they run tirelessly around the face. And yet, it seems to me that time has stopped. How long have I been here ? I cannot say, some weeks, some months maybe. And during this entire time I have had nothing to do, except to look at this clock. But I have lost track of time. Here, the lights can be turned on anytime, regardless of the hour. One can never know whether it is day or night, the only hint is the clock, but it may be broken, there is no way to be sure. I used to have a beautiful watch from my grandfather, but of course they took it away from me when I arrived here. Quarter past five. Is it five am or five pm ? How strange not to be able to know what time it is when one used to care so much about time. And I had always been on time, except one day, that day when everything changed.
\\
\\
My name is Bart Hibitew. I lived in a pretty house near London, with all the comfort I needed. I had a great garden, with a vegetable plot where I used to grow tomatoes, radishes and carrots. I loved to spend my time off cultivating these vegetables and cooking them. They were delicious. The house also had a lovely living room with a fireplace, where I liked to spend my winter evenings, reading quietly, as I had neither wife nor children to bother me.\\
\\
And now here I am, in this cold empty cell, looking at the clock through the bars. And I do not have fresh vegetables to eat anymore. Usually the wardens come once a day, with some food they just get out of the can. It does not look like or taste like food, it is just some kind of mush made with all the things that nobody wants to eat. And they bring it to me whenever they think of it. It can be the morning or the evening they do not care, as long as I am not dying of starvation. What did I do to deserve that ?\\
\\
Each morning I would wake up at six o'clock. I had some kind of internal clock which would wake me up always at the right time. Then I would have a good breakfast to be in shape the whole day, and I would leave my house after a short glance at me through the looking glass to be sure that I was fit to be seen. Then, I would walk for 30 minutes to reach the place where I worked. I had a job that may seem a bit obsolete or degrading, but I liked it a lot. Of course my parents had never understood why I did it and they thought it was a shame to have a servant in the family. But I was not any servant, I was the head of the servants: a chamberlain. What is more I worked for an honourable family. They were of some royal line and had a lot of servants who were under my command. I was very proud of my job and I did it very seriously. I think that is why I managed to keep this job so long while the master's wife was not used to keeping a chamberlain more than a few weeks. They had a beautiful house with many rooms and a huge garden where the mistress of the house would organize parties when her husband was working. She had no true friends, but her name attracted all the social climbers of the region, who were quite numerous. They used to have tea and play cards in the living room during winter, and to play croquet in the garden when the summer came.\\
\\
How long has it been since I saw the sun for the last time ? The first days when I was here, they allowed me to leave my cell once a day. For ten or fifteen minutes, I could enjoy the sight of the sun and the fresh air of the wind. But week after week the walks became scarce and now I am not sure of being able to remember what the sun looks like or how the wind feels. Why am I here ? I have never hurt anybody. I would not be able to hurt someone even if I wanted to, I am far too small and light-weight. And I have always behaved impeccably, so why had they imprisoned me ? I have already spent weeks here and I don't know how many more I will have to spend, looking at this clock. Nobody ever comes to visit me and I spend my days alone with my thoughts, trying to figure out when things had begun to go wrong.\\
\\
Maybe I should have seen this coming. I had never been late in my whole life, my internal clock had always woken me on time, except that day. I should have seen it as a warning, but I was really in a stew -the first time of my life I was overdue - and I didn't take it into account. I jumped out of bed, put on the first clothes I found, grabbed my jacket and ran into the street, without taking the time to look at my appearance in the mirror. Happily, the master was already gone when I arrived and his wife was still sleeping, so nobody noticed my lateness except the cat. It was just a cat, it couldn't say anything to anybody, but I can swear it had an expression like a grin when it saw me sweating in my jacket, trying to catch my breath. I know these were not rational thoughts but this cat had always frightened me and I was worried it could find a way to tell his mistress about my lateness.\\
\\
At least here I am safe from its claws. The clock rings. Six o'clock. I have not looked at the clock for the past three quarters, that is a feat. But the only thing that can make me forget about the clock is thinking about what happened, and now I am left with all my questions. How long will I be kept here ? Why am I here ? Why do they keep me alone ? I am not dangerous, but I am suffering from loneliness. I think I would prefer to hear the ultimate sentence - “Off with his head!” - rather than this never-ending silence with just the tick-tock of the clock. At least my torment would end. Please, let me see someone, I am tired of having this clock for my only companion. Give me at least my grandfather's watch back if you want to leave me alone.\\
\\
In fact this may have been the first signal. The day before, my watch broke down. As I have already said, it was a beautiful watch I got from my grandfather and I cared a lot about it. I had a neighbour who had been watchmaker - he was now retired and had a crazy passion for hats - so I immediately brought him my watch. I had to bear all his chatter when he was working but finally, he managed to fix it. There were not more than two hours between the time when I noticed my watch was broken and the time when I was back in my house with my watch fixed, so this event did not really worry me. I should have been on guard, but I just spent my evening quietly, as I always do. Maybe I didn't want to see it - the broken watch, the lateness. I had always led a quiet life and I didn't want it to change.\\
\\
There was a girl, she used to bring me my meal in the beginning, but now it is almost always the man who brings it to me. He is the only person I see during the whole day. Henry Liddell, an impressive man with a small moustache. He is always wearing a jacket, like I used to do. He is not a bad man but he never talks to me. He just puts my meal on the floor and goes back, without speaking or even looking at me. It is as if I wasn't there. But if I wasn't there you would not bring food Henry, would you ? So please, look at me. I am tired of feeling alone even when you are here.\\ 
There was this girl, I liked her. Of course it is because of her I am here, so I hated her during the first days, but it is not the case anymore -maybe it is the Stockholm syndrome. There was at least one thing that made me like her : she has been the only one who talks to me since my imprisonment. The two others act as if I was not there and this makes me feel very lonely and despaired. But she talked to me. It was just a few minutes per day, but during this time I felt alive again. She was not always nice to me, sometimes she called me with ridiculous names, or she reprimanded me, but at least she was acting as if I was alive. These few minutes really were the best moments of my days. I would spend 23 hours and 55 minutes a day, looking at the clock, waiting for her. But it has been a long time since I have seen her. I think she ended up being bored by me. Maybe she thought I would answer her. I tried but I did not manage to speak, I could only think. I am doomed to be my only interlocutor. But that is not a reason to act as if I was not there!\\
\\
I saw that girl for the first time while I was running in the street, after oversleeping. She was nine or ten, blond, with a lovely blue dress and quite tall for her age. I don't know why I noticed her, whereas I was in a hurry. She behaved strangely, as if she was lost. But I could not stop to help her, I had to rush. What is more, I have never had lot of compassion for lost people. If you are a little organized, you never go to a unknown place without a map. So I went on running, and thanks to that I was only ten minutes late to work and nobody noticed it. I spent my entire morning organising the party my mistress wanted to have in the afternoon. I verified that the cooks were doing their job, and that the gardeners had made a beautiful garden. These were the first sunny days of spring and the lady was likely to want to play croquet with her guests. I thought everything was alright. However, at the start of the afternoon, I noticed that the first roses that were coming up on the rose bushes were white. They were rose bushes we had planted a few months before, and the lady had insisted on the fact that she wanted red roses. I called the gardeners but they were as surprised as I by the colour of the roses. Nobody had a solution, except one of them who stupidly suggested that we could paint all the white roses red. As there was no clever suggestion, we decided first to cut all the roses so that the lady would not notice them during the party, and then to try to find a solution before the next party. I was cutting the roses when I saw the girl again. She still looked lost and she was entering the property. I hurried to tell her to go back before the mistress of the house saw her. She did not like people who enter the property without her agreement, and was easily angered. Moreover, I had already had enough problems for the day with my lateness of the morning -which I was sure the cat had found a way to tell her- and the roses which turned out to be white instead of red. I was already pretty sure I would lose my job, but I did not want to lose more. While I was explaining all that to the girl, trying to make her go away, she looked at me with a smile, caught me by the ears and ran out of the grounds. I was relieved that she had exited the garden, but when I asked her why she was bringing me with her she did not answer.\\
\\
Here she comes, with my meal. It has been weeks since I have seen her and today she comes. I should think of her more often if it makes her come.\\
"Here is your food mister rabbit!  You still don't talk, do you ?"\\
"Of course not Alice, I cannot talk in this world. If I could I would have asked you all the questions that have occupied my mind for months now."\\
"Everyone says that I am a liar because of you. I told them I had a speaking rabbit but in fact you were just an ordinary rabbit."\\
"I am not ordinary, I am chamberlain."\\
"Well, if you don't want to talk you have nothing to do here anymore."\\
\\
She opens the cage's door and catches me by the ears again. She brings me in front of the clock, always hanging by my ears. Twenty to seven. Why does she bring me here ? I know this clock. Well, maybe not in fact. There is something behind the hands I had never seen before. This is very small, but it is my room, I am pretty sure. And in the bed, I am sleeping.\\
\\
I open my eyes. I am in my bed, in my house, in my world. Was it just a bad dream ? Here is my watch. Twenty to seven! I am late. No time to say hello, good bye, I'm late I'm late I'm late.


\end{document}